XXX

### 2012-03-24 paper/engNERwiki.tex
I don't know.

The procedure described in the last section was used to generate the Hungarian corpus as well. However, the differences between English and Hungarian prompted XXX several modifications in its steps. In this section we describe how the algorithm was adapted to Hungarian. XXX!!!

@@

@@

according to the Szeged NER guideline

>>>>

Hungarian differs from English not only as a language, but in data and tool coverage and NER practices as well.
The procedure described in the previous section was used to generate the Hungarian corpus as well. However, the differences between English and Hungarian prompted XXX several modifications in its steps. In this section we describe how the algorithm was adapted to Hungarian. XXX!!!

@@

\subsection{Training Corpus}

@@
